Towards End-user Web Scraping For Customization

### 2021-03-14 paper.tex
Changes to 3.2 and minor wording changes in other parts

While each of these principles has been explored in prior work, our
contribution in this work is combining them into a novel application to
the domain of end user web scraping and customization.

@@

The idea of ``liveness'' in programming can be traced back to Tanimoto's
work on VIVA \citep{tanimoto1990}. It generally describes programming
environments in which programmers receive immediate feedback about a
program while it is being created. In the context of Wildcard, adapters
are the program, the table interface is the output of the program and
the highlighting on the website is the visual representation of the
program. Live programming in our system is implemented by continually
re-generating an adapter based on the DOM element under the user's
cursor and the previous demonstrations if any, reverting if the user
hovers away and committing when the user clicks. The row and column
selectors generated during the wrapper induction process are used to
highlight all the matching elements on the website and create an
adapter. Highlighting all the matching column elements on the website
provides visual feedback about the system's generalization to the user.
Creating an adapter enables the system to populate the table view and
set up the bidirectional synchronization. Because the table is populated
and the bidirectional synchronization is set up, users can customize as
they scrape. Live programming is possible in our system because the
wrapper induction algorithm and adapters execute very quickly. We have
yet to benchmark the performance in detail and compare it to other
end-user web scraping systems like FlashProg \citep{mayer2015} that
offer live programming environments.

@@

Like existing programming-by-demonstration approaches, web scraping in
our current implementation is limited to what can be demonstrated by
point-and-click. More generally, this surfaces a fundamental limitation
of programming-by-demonstration: the inability to specify logic. One
solution for this is taking advantage of spreadsheet formulas which have
enabled millions of end-users to specify logic. Because of this,
Wildcard already includes a spreadsheet-like formula language for
specifying customizations. We plan to extend this language to augment
our demonstration-based web scraping with the goal of raising the
ceiling on the expressiveness available to end-users. One concrete use
case for this is scraping DOM element attributes which cannot be
demonstrated by point-and-click but contain valuable data. For example,
link elements have an \emph{href} attribute which contain the URLs
associated with the link element and video elements have
\emph{currentTime} and \emph{duration} attributes which contain data
about the current playback position and duration respectively. This use
of spreadsheet-like formulas to specify logic is related to approaches
taken by Microsoft Power Apps \citep{zotero-94}, Glide
\citep{zotero-108}, Coda \citep{zotero-110} and Gneiss
\citep{chang2014}.

>>>>

While each of these principles has been explored in prior work by
various researchers, our contribution in this work is combining them in
a novel way for the domain of end-user web scraping and customization.

@@

The idea of ``liveness'' in programming can be traced back to Tanimoto's
work on VIVA \citep{tanimoto1990}. It generally describes programming
environments in which programmers receive immediate feedback about a
program while it is being created. In the context of Wildcard, adapters
are the program, the table interface is the output of the program and
the highlighting on the website is the visual representation of the
program.

Live programming in our system is implemented by continually
re-generating an adapter based on the DOM element under the user's
cursor and the previous demonstrations if any, reverting if the user
hovers away and committing when the user clicks. The row and column
selectors generated during the wrapper induction process are used to
highlight all the matching elements on the website and create an
adapter. Highlighting all the matching column elements on the website
provides visual feedback about the system's generalization to the user.
Creating an adapter enables the system to populate the table view and
set up the bidirectional synchronization. Because the table is populated
and the bidirectional synchronization is set up, users can customize as
they scrape. Live programming is possible in our system because the
wrapper induction algorithm and adapters execute very quickly. We have
yet to benchmark the performance in detail and compare it to other
end-user web scraping systems like FlashProg \citep{mayer2015} that
offer live programming environments.

@@

Like existing programming-by-demonstration approaches, web scraping in
our current implementation is limited to what can be demonstrated by
point-and-click. More generally, this surfaces a fundamental limitation
of programming-by-demonstration: the inability to specify logic. One
solution for this is taking advantage of spreadsheet formulas which have
enabled millions of end-users to specify logic. Because of this,
Wildcard already includes a spreadsheet-like formula language for
specifying customizations. We plan to extend this language to augment
our demonstration-based web scraping with the goal of raising the
ceiling on the expressiveness available to end-users. One concrete use
case for this is scraping DOM element attributes which cannot be
demonstrated by point-and-click but contain valuable data. For example,
link elements have an \emph{href} attribute which contain the URLs
associated with the link element and video elements have
\emph{currentTime} and \emph{duration} attributes which contain data
about the current playback position and duration respectively. This use
of spreadsheet-like formulas to enable end-users to specify logic is
related to approaches taken by Microsoft Power Apps \citep{zotero-94},
Glide \citep{zotero-108}, Coda \citep{zotero-110} and Gneiss
\citep{chang2014}.
